%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Computational Algorithms Project Monitor} % Job title
    {CEFET/RJ} % Organization
    {Rio de Janeiro, Brazil} % Location
    {Aug. 2019 - Aug. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Taught about program implementation in C, C++ and Python Languages.}
        \item {Taught about basic data structures (array, matrix and queue).}
        \item {Helped teacher with tasks.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Discrete Mathematics Monitor} % Job title
    {CEFET/RJ} % Organization
    {Rio de Janeiro, Brazil} % Location
    {Aug. 2020 - Feb. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Taught about Set Theory, functions, graphs and others topics.}
        \item {Helped teacher with tasks.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Frontend Developer} % Job title
    {Bluemoon Co., Ltd.} % Organization
    {Rio de Janeiro, Brazil} % Location
    {Jun. 2021 - Jul. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and developed several forms pages in corporation CRMs using Angular, HTML and SASS with Backend integration.}
        \item {Developed several Frontend validators for data handled by forms.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Fullstack Developer} % Job title
    {Bluemoon Co., Ltd.} % Organization
    {Rio de Janeiro, Brazil} % Location
    {Jul. 2021 -  Aug. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Handled all tasks from above job.}
        \item {Developed several new Backend features using NestJS, Knex.JS, TypeORM, Prisma and MySQL.}
        \item {Developed several external API integrations with Backend and Frontend.}
        \item {Designed and developed several dashboards for the corporation CRMs.}
        \item {Designed, developed and deployed several MySQL databases.}
        \item {Managed database performance and backups.}
        \item {Developed several CRONs (scheduled jobs).}
        \item {Developed CRM integration with corporation communication media (Slack and WhatsApp).}
        \item {Helped in a web crawler development written on python.}
        \item {Helped in CRMs CI/CD configuration using Heroku, Vercel, AWS and Docker.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
